Manuscript Figures

### 2018-06-08 Manuscript Figures.Rmd
Methods to sort pattern types in expression and abundance

>>>>

```{r extra6, echo=FALSE, warning=FALSE, message=FALSE, fig.width=4, fig.height=4, fig.align='center'}
## Not really a plot yet... just sorting types
source("./R/analysis/functionalDivergence_func.R")
"gene"
gene.pair.types <- getTypeSort(homeologs.pairs, maize.walley.v4mapped.expression, 2, .95)
summary(as.factor(gene.pair.types$type))
"protein"
protein.pair.types <- getTypeSortProteins(homeologs.pairs, maize.walley.abundance.v4, 2, .95)
summary(as.factor(protein.pair.types$type))
"agree"
summary(as.factor(intersect(gene.pair.types, protein.pair.types)$type))

# intersect(gene.pair.types[!gene.pair.types$type %in% c("ambiguous"),], protein.pair.types[!protein.pair.types$type %in% c("ambiguous"),])
# #dead expression and still dead abundance (17/297)
# protein.pair.types[protein.pair.types$Maize1 %in% gene.pair.types$Maize1[gene.pair.types$type %in% c("1dead","2dead")],] %>% subset(type %in% c("1dead","2dead"))
```
